---
title: "app_preparation"
author: "Katie Willi"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sf)
sf::sf_use_s2(FALSE)
```

NPS Park Boundary Data, aggregated by UNIT_CODE//PARK NAME
```{r}
colors = data.frame(
  Assessment_Category = c("Impaired", "Good", "Unknown", "No State Data", "No Water Features"),
  col = c("#DC851E", "#059FA4", "#A1A522", "#C2CAD7", NA),
  dark_col = c("#813B00", "#005258", "#4F5900", "#5A616D", NA),
  Priority = c(1, 2, 3, 4, 5))

parks <- sf::st_read('data/in/nps_boundary.shp') %>%
  st_transform(4326)

park_table <- sf::st_read('data/in/nps_boundary.shp') %>%
  st_drop_geometry() 

boundary_lines <- nps_points <-  sf::st_read('data/in/nps_boundary.shp') %>%
  rename(Park = UNIT_NAME) %>%
  st_zm() %>%
  sf::st_cast("MULTILINESTRING") %>%
  st_transform(4326) %>%
  dplyr::select(UNIT_CODE, Park)
saveRDS(boundary_lines, 'shiny/data/nps_boundary_lines.RDS')
```

Linking the HIS-ORW information to NHD-HR flowlines:
```{r}
# For every park, join ORW info to the NHD.
orw_only <- readRDS('data/mid/parks_with_orw.RDS')

nhdhr_park_flows_and_orw <- readRDS('data/mid/nhdhr_park_flow.RDS') %>%
  mutate(reachcode = as.numeric(ReachCode)) %>%
  sp::merge(orw_only, by = "reachcode", all.x = TRUE)

# Turns out HIS is based on an outdated NHD HR version, so some of the datasets reference ReachCodes that no longer exist. 
# I did all sorts of research on how best to access the underlying geospatial layers from the .mdb's in R, but had no luck. 
# Therefore I had to manually convert each .mdb into a shapefile in ArcGIS Desktop.

didnt_work <- anti_join(orw_only, filter(nhdhr_park_flows_and_orw, !is.na(Tier)), by = "reachcode") %>%
  mutate(gnis_id = as.character(gnis_id))

bad_puller <- function(baddies){
  
  data <- st_read(dsn = 'data/mid/arc_his/ArcHIS.gdb', layer = baddies) %>%
    st_transform(4326) %>%
    st_zm() %>%
    select(contains("reachcode", ignore.case = TRUE)) %>%
    rename(reachcode = 1) %>%
    mutate(reachcode=as.numeric(reachcode)) %>%
    rename(geometry = 2) %>%
    inner_join(orw_only, by = "reachcode") %>%
    st_intersection(., select(parks, UNIT_CODE))
  
  return(data)
  
}

# These are the parks whose NHD HR has been altered since NPS's last HIS workflow. Their raw flowlines shapefile features
# embedded in the mdb were manually transformed to shapefiles in ArcGIS Desktop.

baddies <- c("ACAD", "APPA", "BICA", "BICY", "BISC", "BISO", "BLRI", "BRCA", "BUFF", "CAHA", "CANA", "CONG", "CUVA", "DELA", 
             "DEWA", "DINO", "DRTO", "EVER", "GARI", "GLAC", "GRSM", "GRTE", "GUIS", "HOCU", "INDU", "ISRO", "MACA", "MEVE", 
             "MISS", "MNRR", "MORR", "NATR", "NERI", "OBRI", "PIRO", "ROMO", "SHIL", "SLBE", "TIMU", "UPDE", "VIIS", "VOYA", 
             "YELL") %>%
  
  map(~bad_puller(.)) %>%
  bind_rows()

all_orw_data <- bind_rows(st_transform(nhdhr_park_flows_and_orw, 4326), baddies) %>%
  filter(!is.na(Tier)) %>% 
  select(reachcode, UNIT_CODE, Tier, entire_extent_of_orw, designation_name)

orw <- all_orw_data %>%
  dplyr::filter(!is.na(Tier)) %>% 
  left_join(park_table, by = "UNIT_CODE") %>% 
  rename(Park = UNIT_NAME) %>% 
  st_simplify(dTolerance = 10) %>%
  group_by(UNIT_CODE, Park, STATE, Tier, designation_name, entire_extent_of_orw) %>%
  summarize() %>%
  rename(State = STATE)
saveRDS(orw, 'shiny/data/orw_.RDS')
```

Getting raw NHD-HR features for mapping where water is located in parks:
```{r}
flowlines <- readRDS('data/mid/nhdhr_park_flow.RDS') %>%
  group_by(UNIT_CODE) %>%
  summarize() %>%
  left_join(park_table, by = "UNIT_CODE") %>%
  sf::st_simplify(dTolerance = 10) %>%
  st_transform(4326) %>%
  dplyr::select(UNIT_NAME, STATE)
saveRDS(flowlines, 'shiny/data/map_flowlines.RDS')
areas <- readRDS('data/mid/nhdhr_park_area.RDS') %>%
  group_by(UNIT_CODE) %>%
  summarize() %>%
  left_join(park_table, by = "UNIT_CODE") %>%
  sf::st_simplify(dTolerance = 10) %>%
  st_transform(4326) %>%
  select(UNIT_NAME, STATE)
saveRDS(areas, 'shiny/data/map_areas.RDS')
waterbodies <- readRDS('data/mid/nhdhr_park_waterbody.RDS') %>%
  group_by(UNIT_CODE) %>%
  summarize() %>%
  sf::st_simplify(dTolerance = 10) %>%
  left_join(park_table, by = "UNIT_CODE") %>% 
  st_transform(4326) %>%
  select(UNIT_NAME, STATE)
saveRDS(waterbodies, 'shiny/data/map_waterbodies.RDS')
```

Find catchments without water features, so that we can remove them from the app:
```{r}
no_water <- parks %>%
  filter(!STATE %in% c("AK","HI","PR","VI","AS","GU","MP")) %>%
  # this is a weird lil park in the Middle of Lake Erie:
  filter(UNIT_CODE != "PEVI") %>%
  # clipped water features from the NHD HR:
  filter(!UNIT_CODE %in% readRDS('data/mid/nhdhr_park_area.RDS')$UNIT_CODE) %>%
  filter(!UNIT_CODE %in% readRDS('data/mid/nhdhr_park_flow.RDS')$UNIT_CODE) %>%
  filter(!UNIT_CODE %in% readRDS('data/mid/nhdhr_park_waterbody.RDS')$UNIT_CODE) %>%
  bind_rows(filter(parks, UNIT_NAME %in% read_csv('data/in/no_water_parks.csv')$UNIT_NAME)) %>%
  distinct(UNIT_NAME, .keep_all = TRUE) %>%
  mutate(hydro = "No Water Features")

# CATCHMENT DATA #

park_catch <- readRDS('data/mid/final_raw_catch.RDS') %>%
  left_join(., st_drop_geometry(parks), by = "UNIT_CODE") %>%
  mutate(nhdplusid = as.character(nhdplusid)) %>%
  select(UNIT_CODE, UNIT_NAME, nhdplusid, CATCH_TYPE)

park_empty_catch_1 <- park_catch %>%
  .[readRDS('data/mid/nhdhr_park_area.RDS'),]

park_empty_catch_2 <- park_catch %>%
  .[readRDS('data/mid/nhdhr_park_flow.RDS'),]

park_empty_catch_3 <- park_catch %>%
  .[readRDS('data/mid/nhdhr_park_waterbody.RDS'),]

empty_catch <- park_catch %>% 
  filter(CATCH_TYPE == "NHDPlusHR") %>%
  filter(!nhdplusid %in% park_empty_catch_1$nhdplusid) %>%
  filter(!nhdplusid %in% park_empty_catch_2$nhdplusid) %>%
  filter(!nhdplusid %in% park_empty_catch_3$nhdplusid)

```

Catchment-level ATTAINS data:
```{r}
nps_all_attains <- readRDS('data/mid/nps_attains_catchment_table_.RDS') %>%
  left_join(., park_table, by = "UNIT_CODE")  %>%
  mutate(nhdplusid = as.character(nhdplusid)) %>%
  select(UNIT_NAME, office, nhdplusid, parametername, ircategory, parametercategorycode)

impaired_list <- nps_all_attains %>%
  dplyr::filter(parametercategorycode %in% c("5A","5","4C","4B","4A")) %>% 
  filter(!UNIT_NAME %in% no_water$UNIT_NAME) %>%
  group_by(nhdplusid, UNIT_NAME) %>%
  summarize(Impairments = as.character(list(unique(parametername))),
            Assessment_Category = "Impaired",
            Office = list(unique(office)))

good_list <- nps_all_attains %>%
  dplyr::filter(ircategory %in% c("1","2")) %>% 
  dplyr::filter(!nhdplusid %in% impaired_list$nhdplusid) %>%
  filter(!UNIT_NAME %in% no_water$UNIT_NAME) %>%
  group_by(nhdplusid, UNIT_NAME) %>%
  summarize(Impairments = "None",
            Assessment_Category = "Good",
            Office = list(unique(office)))

unknown_list <- nps_all_attains %>%
  dplyr::filter(ircategory %in% c("3")) %>% 
  dplyr::filter(!nhdplusid %in% impaired_list$nhdplusid) %>%
  dplyr::filter(!nhdplusid %in% good_list$nhdplusid) %>%
  filter(!UNIT_NAME %in% no_water$UNIT_NAME) %>%
  group_by(nhdplusid, UNIT_NAME) %>%
  summarize(Impairments = "Unknown",
            Assessment_Category = "Unknown",
            Office = list(unique(office)))

attains <- bind_rows(impaired_list, good_list, unknown_list)

for_app <- park_catch %>%
  left_join(., attains, by=c("nhdplusid", "UNIT_NAME")) %>% 
  mutate(Assessment_Category =  ifelse(UNIT_NAME %in% no_water$UNIT_NAME, "No Water Features",
                                       ifelse(is.na(Assessment_Category) & nhdplusid %in% empty_catch$nhdplusid, "No Water Features",
                                              ifelse(is.na(Assessment_Category) & !nhdplusid %in% empty_catch$nhdplusid, "No State Data", Assessment_Category)))) %>%
  sp::merge(colors, by ="Assessment_Category") %>%
  dplyr::rename(Park = UNIT_NAME) %>% 
  left_join(st_drop_geometry(parks), by=c("Park" = "UNIT_NAME")) %>%
  filter(!STATE %in% c("AK","HI","PR","VI","AS","GU","MP")) %>%
  st_transform(4326) 

for_app$catchment_area <- sf::st_area(for_app, by_element = TRUE)

for_app <- for_app %>%
  select(Assessment_Category, Park, nhdplusid, Impairments, catchment_area, col) %>%
  sf::st_simplify(dTolerance = 0.0001)

saveRDS(for_app, 'shiny/data/catch.RDS')
```

Raw geospatial ATTAINS features in parks
```{r}
# PARK ATTAINS #
park_point_impaired <- readRDS('data/mid/nps_attains_park_point_.RDS') %>%
  dplyr::left_join(.,
                   # remove duplicate/unnecessary columns:
                   dplyr::select(readRDS('data/mid/attains_au_assmnt_parms.RDS'), 
                                 -c(assmnt_joinkey, organizationid, submissionid, orgtype, tas303d, reportingcycle, waterbodyreportlink, GLOBALID)),
                   by = "assessmentunitidentifier", multiple = "all") %>%
  dplyr::filter(parametercategorycode %in% c("5A","5","4C","4B","4A")) %>% 
  filter(!UNIT_NAME %in% no_water$UNIT_NAME) %>%
  group_by(assessmentunitidentifier, UNIT_NAME, state, reportingcycle) %>%
  summarize(Impairments = as.character(list(unique(parametername))),
            Assessment_Category = "Impaired",
            Link = as.character(list(unique(waterbodyreportlink)))) %>% 
  mutate(Impairments = gsub('"', "", Impairments)) %>%
  mutate(Impairments = gsub("^c\\(|\\)$", "", Impairments)) %>%
  left_join(colors, by = "Assessment_Category") %>%
  select(Park = UNIT_NAME,
         State = state,
         reportingcycle = reportingcycle,
         assessmentunitidentifier,
         Assessment_Category,
         Link,
         Impairments,
         col, 
         dark_col) %>% 
  sf::st_simplify(dTolerance = 10) %>%
  st_transform(4326)

park_point_good <- readRDS('data/mid/nps_attains_park_point_.RDS') %>%
  dplyr::left_join(.,
                   # remove duplicate/unnecessary columns:
                   dplyr::select(readRDS('data/mid/attains_au_assmnt_parms.RDS'), 
                                 -c(assmnt_joinkey, organizationid, submissionid, orgtype, tas303d, reportingcycle, waterbodyreportlink, GLOBALID)),
                   by = "assessmentunitidentifier", multiple = "all") %>%
  dplyr::filter(!assessmentunitidentifier %in% park_point_impaired$assessmentunitidentifier) %>%
  dplyr::filter(ircategory %in% c("1","2")) %>% 
  filter(!UNIT_NAME %in% no_water$UNIT_NAME) %>%
  group_by(assessmentunitidentifier, UNIT_NAME, state, reportingcycle) %>%
  summarize(Impairments = "None",
            Assessment_Category = "Good",
            Link = as.character(list(unique(waterbodyreportlink)))) %>% 
  left_join(colors, by = "Assessment_Category") %>%
  select(Park = UNIT_NAME,
         State = state,
         reportingcycle = reportingcycle,
         assessmentunitidentifier,
         Assessment_Category,
         Link,
         Impairments,
         col, 
         dark_col) %>% 
  sf::st_simplify(dTolerance = 10) %>%
  st_transform(4326)

park_point_unknown <- readRDS('data/mid/nps_attains_park_point.RDS') %>%
  dplyr::left_join(.,
                   # remove duplicate/unnecessary columns:
                   dplyr::select(readRDS('data/mid/attains_au_assmnt_parms.RDS'),
                                 -c(assmnt_joinkey, organizationid, submissionid, orgtype, tas303d, reportingcycle, waterbodyreportlink, GLOBALID)),
                   by = "assessmentunitidentifier", multiple = "all") %>%
  dplyr::filter(!assessmentunitidentifier %in% park_point_impaired$assessmentunitidentifier) %>%
  dplyr::filter(!assessmentunitidentifier %in% park_point_good$assessmentunitidentifier) %>%
  dplyr::filter(ircategory %in% c("3")) %>% 
  filter(!UNIT_NAME %in% no_water$UNIT_NAME) %>%
  group_by(assessmentunitidentifier, UNIT_NAME, state, reportingcycle) %>%
  summarize(Impairments = "Unknown",
            Assessment_Category = "Unknown",
            Link = as.character(list(unique(waterbodyreportlink)))) %>% 
  left_join(colors, by = "Assessment_Category") %>%
  select(Park = UNIT_NAME,
         State = state,
         reportingcycle = reportingcycle,
         assessmentunitidentifier,
         Assessment_Category,
         Link,
         Impairments,
         col, 
         dark_col) %>% 
  sf::st_simplify(dTolerance = 10) %>%
  st_transform(4326)

park_points <- bind_rows(park_point_impaired, park_point_good) %>% #, park_point_unknown) %>%
  filter(!Park %in% no_water$UNIT_NAME) %>%
  mutate(TYPE = "Point")
saveRDS(park_points, 'shiny/data/points.RDS')

# AREA #

park_area_impaired <- readRDS('data/mid/nps_attains_park_area_.RDS') %>%
  dplyr::left_join(.,
                   # remove duplicate/unnecessary columns:
                   dplyr::select(readRDS('data/mid/attains_au_assmnt_parms.RDS'), 
                                 -c(assmnt_joinkey, organizationid, submissionid, orgtype, tas303d, reportingcycle, waterbodyreportlink, GLOBALID)),
                   by = "assessmentunitidentifier", multiple = "all") %>%
  dplyr::filter(parametercategorycode %in% c("5A","5","4C","4B","4A")) %>% 
  filter(!UNIT_NAME %in% no_water$UNIT_NAME) %>%
  group_by(assessmentunitidentifier, UNIT_NAME, state, reportingcycle) %>%
  summarize(Impairments = as.character(list(unique(parametername))),
            Assessment_Category = "Impaired",
            Link = as.character(list(unique(waterbodyreportlink)))) %>% 
  mutate(Impairments = gsub('"', "", Impairments)) %>%
  mutate(Impairments = gsub("^c\\(|\\)$", "", Impairments)) %>%
  left_join(colors, by = "Assessment_Category") %>%
  select(Park = UNIT_NAME,
         State = state,
         reportingcycle = reportingcycle,
         assessmentunitidentifier,
         Assessment_Category,
         Link,
         Impairments,
         col, 
         dark_col) %>% 
  sf::st_simplify(dTolerance = 10) %>%
  st_transform(4326)

park_area_good <- readRDS('data/mid/nps_attains_park_area_.RDS') %>%
  dplyr::left_join(.,
                   # remove duplicate/unnecessary columns:
                   dplyr::select(readRDS('data/mid/attains_au_assmnt_parms.RDS'),
                                 -c(assmnt_joinkey, organizationid, submissionid, orgtype, tas303d, reportingcycle, waterbodyreportlink, GLOBALID)),
                   by = "assessmentunitidentifier", multiple = "all") %>%
  dplyr::filter(!assessmentunitidentifier %in% park_area_impaired$assessmentunitidentifier) %>%
  dplyr::filter(ircategory %in% c("1","2")) %>% 
  filter(!UNIT_NAME %in% no_water$UNIT_NAME) %>%
  group_by(assessmentunitidentifier, UNIT_NAME, state, reportingcycle) %>%
  summarize(Impairments = "None",
            Assessment_Category = "Good",
            Link = as.character(list(unique(waterbodyreportlink)))) %>% 
  left_join(colors, by = "Assessment_Category") %>%
  select(Park = UNIT_NAME,
         State = state,
         reportingcycle = reportingcycle,
         assessmentunitidentifier,
         Assessment_Category,
         Link,
         Impairments,
         col, 
         dark_col) %>% 
  sf::st_simplify(dTolerance = 10) %>%
  st_transform(4326)

park_area_unknown <- readRDS('data/mid/nps_attains_park_area_.RDS') %>%
  dplyr::left_join(.,
                   # remove duplicate/unnecessary columns:
                   dplyr::select(readRDS('data/mid/attains_au_assmnt_parms.RDS'), 
                                 -c(assmnt_joinkey, organizationid, submissionid, orgtype, tas303d, reportingcycle, waterbodyreportlink, GLOBALID)),
                   by = "assessmentunitidentifier", multiple = "all") %>%
  dplyr::filter(!assessmentunitidentifier %in% park_area_impaired$assessmentunitidentifier) %>%
  dplyr::filter(!assessmentunitidentifier %in% park_area_good$assessmentunitidentifier) %>%
  dplyr::filter(ircategory %in% c("3")) %>%
  filter(!UNIT_NAME %in% no_water$UNIT_NAME) %>%
  group_by(assessmentunitidentifier, UNIT_NAME, state, reportingcycle) %>%
  summarize(Impairments = "Unknown",
            Assessment_Category = "Unknown",
            Link = as.character(list(unique(waterbodyreportlink)))) %>% 
  left_join(colors, by = "Assessment_Category") %>%
  select(Park = UNIT_NAME,
         State = state,
         reportingcycle = reportingcycle,
         assessmentunitidentifier,
         Assessment_Category,
         Link,
         Impairments,
         col, 
         dark_col) %>% 
  sf::st_simplify(dTolerance = 10) %>%
  st_transform(4326)

park_areas <- bind_rows(park_area_impaired, park_area_good, park_area_unknown) %>%
  filter(!Park %in% no_water$UNIT_NAME) %>%
  mutate(TYPE = "Area")
saveRDS(park_areas, 'shiny/data/areas.RDS')

# LINE #

park_line_impaired <- readRDS('data/mid/nps_attains_park_line_.RDS') %>%
  dplyr::left_join(.,
                   # remove duplicate/unnecessary columns:
                   dplyr::select(readRDS('data/mid/attains_au_assmnt_parms.RDS'),
                                 -c(assmnt_joinkey, organizationid, submissionid, orgtype, tas303d, reportingcycle, waterbodyreportlink, GLOBALID)),
                   by = "assessmentunitidentifier", multiple = "all") %>%
  dplyr::filter(parametercategorycode %in% c("5A","5","4C","4B","4A")) %>% 
  filter(!UNIT_NAME %in% no_water$UNIT_NAME) %>%
  group_by(assessmentunitidentifier, UNIT_NAME, state, reportingcycle) %>%
  summarize(Impairments = as.character(list(unique(parametername))),
            Assessment_Category = "Impaired",
            Link = as.character(list(unique(waterbodyreportlink)))) %>% 
  left_join(colors, by = "Assessment_Category") %>%
  mutate(Impairments = gsub('"', "", Impairments)) %>%
  mutate(Impairments = gsub("^c\\(|\\)$", "", Impairments)) %>%
  select(Park = UNIT_NAME,
         State = state,
         reportingcycle = reportingcycle,
         assessmentunitidentifier,
         Assessment_Category,
         Link,
         Impairments,
         col, 
         dark_col) %>% 
  sf::st_simplify(dTolerance = 10) %>%
  st_transform(4326)

park_line_good <- readRDS('data/mid/nps_attains_park_line_.RDS') %>%
  dplyr::left_join(.,
                   # remove duplicate/unnecessary columns:
                   dplyr::select(readRDS('data/mid/attains_au_assmnt_parms.RDS'), 
                                 -c(assmnt_joinkey, organizationid, submissionid, orgtype, tas303d, reportingcycle, waterbodyreportlink, GLOBALID)),
                   by = "assessmentunitidentifier", multiple = "all") %>%
  dplyr::filter(!assessmentunitidentifier %in% park_line_impaired$assessmentunitidentifier) %>%
  dplyr::filter(ircategory %in% c("1","2")) %>% 
  filter(!UNIT_NAME %in% no_water$UNIT_NAME) %>%
  group_by(assessmentunitidentifier, UNIT_NAME, state, reportingcycle) %>%
  summarize(Impairments = "None",
            Assessment_Category = "Good",
            Link = as.character(list(unique(waterbodyreportlink)))) %>% 
  left_join(colors, by = "Assessment_Category") %>%
  select(Park = UNIT_NAME,
         State = state,
         reportingcycle = reportingcycle,
         assessmentunitidentifier,
         Assessment_Category,
         Link,
         Impairments,
         col, 
         dark_col) %>% 
  sf::st_simplify(dTolerance = 10) %>%
  st_transform(4326)

park_line_unknown <- readRDS('data/mid/nps_attains_park_line_.RDS') %>%
  dplyr::left_join(.,
                   # remove duplicate/unnecessary columns:
                   dplyr::select(readRDS('data/mid/attains_au_assmnt_parms.RDS'), 
                                 -c(assmnt_joinkey, organizationid, submissionid, orgtype, tas303d, reportingcycle, waterbodyreportlink, GLOBALID)),
                   by = "assessmentunitidentifier", multiple = "all") %>%
  dplyr::filter(!assessmentunitidentifier %in% park_line_impaired$assessmentunitidentifier) %>%
  dplyr::filter(!assessmentunitidentifier %in% park_line_good$assessmentunitidentifier) %>%
  dplyr::filter(ircategory %in% c("3")) %>% 
  filter(!UNIT_NAME %in% no_water$UNIT_NAME) %>%
  group_by(assessmentunitidentifier, UNIT_NAME, state, reportingcycle) %>%
  summarize(Impairments = "Unknown",
            Assessment_Category = "Unknown",
            Link = as.character(list(unique(waterbodyreportlink)))) %>% 
  left_join(colors, by = "Assessment_Category") %>%
  select(Park = UNIT_NAME,
         State = state,
         reportingcycle = reportingcycle,
         assessmentunitidentifier,
         Assessment_Category,
         Link,
         Impairments,
         col, 
         dark_col) %>% 
  sf::st_simplify(dTolerance = 10) %>%
  st_transform(4326)

park_lines <- bind_rows(park_line_impaired, park_line_good, park_line_unknown) %>%
  filter(!Park %in% no_water$UNIT_NAME) %>%
  mutate(TYPE = "Line")

saveRDS(park_lines, 'shiny/data/lines.RDS')
```

Downloadable ATTAINS data table by park:
```{r}
npca_regions <- sf::st_read("data/in/npca_regions.shp") 

parks <- sf::st_read('data/in/nps_boundary.shp') %>%
  st_join(npca_regions) %>%
  st_drop_geometry() %>%
  group_by(UNIT_NAME) %>%
  summarize(NPCA_Region = list(unique(office))) %>%
  mutate(NPCA_Region = gsub('"', "", NPCA_Region)) %>%
  mutate(NPCA_Region = gsub("^c\\(|\\)$", "", NPCA_Region)) %>%
  mutate(NPCA_Region = ifelse(is.na(NPCA_Region), "Pacific", NPCA_Region))

attains_table <- bind_rows(st_drop_geometry(park_lines), st_drop_geometry(park_areas), st_drop_geometry(park_points)) %>%
  mutate(Impairments = gsub('"', "", Impairments)) %>%
  mutate(Impairments = gsub("^c\\(|\\)$", "", Impairments)) %>%
  left_join(., parks, by=c("Park" = "UNIT_NAME")) %>%
  select(Park,
         NPCA_Region,
         State,
         Reporting_Cycle = reportingcycle,
         Assessment_Code = assessmentunitidentifier,
         Assessment_Category,
         Impairments,
         URL = Link,
         Type = TYPE) 
saveRDS(attains_table, 'shiny/data/attains_table.RDS')
```

# Park-wide impairment mapper (tab 1):
```{r}
parkwide_all_attains <- readRDS('data/out/nps_all_wq_data_final_.RDS') %>%
  dplyr::filter(parametercategorycode %in% c("5A","5","4C","4B", "4A")) %>%
  mutate(parametergroupname = ifelse(parametergroupname == "METALS (OTHER THAN MERCURY)", "METALS OTHER THAN HG",
                              ifelse(parametergroupname == "POLYCHLORINATED BIPHENYLS (PCBS)", "POLYCHLORINATED BIPHENYLS - PCBS", parametergroupname))) %>%
  select(UNIT_NAME, state, Impairments = parametergroupname) %>%
  group_by(UNIT_NAME, state) %>%
  summarize(Impairments = list(unique(Impairments))) %>%
  mutate(Impairments = gsub('"', "", Impairments)) %>%
  mutate(Impairments = gsub("^c\\(|\\)$", "", Impairments))

nps_points <-  sf::st_read('data/in/nps_boundary.shp') %>%
  left_join(parkwide_all_attains, by = "UNIT_NAME") %>%
  select(Park = UNIT_NAME,
         State = state,
         Impairments) %>%
  sf::st_centroid() %>%
  left_join(distinct(select(readRDS('shiny/data/attains_table.RDS'), Park, NPCA_Region)), by = "Park") %>%
  st_transform(4326)
saveRDS(nps_points, 'shiny/data/nps_points.RDS')
```

```{r}
states <- readRDS('data/mid/states.RDS') %>%
  select(STUSPS, NAME) %>%
  st_transform(4326) %>%
   sf::st_cast("MULTILINESTRING") 
saveRDS(states, 'shiny/data/states.RDS')
```

