---
title: "03 - ATTAINS Statistics by Catchment"
author: "Kathryn Willi"
date: "2023-05-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse) # tidying
library(sf) # geospatial analysis
library(data.table)
library(mapview) # for quickly viewing geospatial data

map(list.files('src/fxn', full.names = TRUE), source)

sf::sf_use_s2(FALSE)

# Load in park boundaries (from NPS IRMA)
parks <- sf::st_read("data/in/nps_boundary.shp") %>%
  # transform to the projection of the NHD:
  sf::st_transform(4269)
``` 

This workflow utilizes the catchment information that we pulled in step 2

Subset and clip all catchments and flowlines within park boundaries. This is done iteratively over individual HUC-4s, because the NHRPlus HR is VERY large, and breaking it up speeds up processing time and reduces risk of crashing.

```{r}
# List of HUC-2s to map over:
hucs <- (c("01","02","03","04","05","06","07","08","09","10",
              "11","12","13","14","15","16","17","18","19","20",
              "21","22"))

figure_it_out <- function(hucs){
  
  # Where to find our HUC-4 datasets:
  nhdhr <- paste0('data/in/nhdplushr/', hucs, "/")
  files <- list.files(nhdhr, pattern = "GDB.gdb", full.names=TRUE)
  
  # Clip NHD-HR features within park units across individual HUC-4 files:
  for(i in 1:length(files)){
     catchments <- sf::st_read(dsn = files[i], layer = "NHDPlusCatchment")
    
    # # filter out and clip the flowline features within the park boundaries:
    catchments <- catchments %>%
      # filter out and clip the catchment features within the park boundaries:
      sf::st_zm() %>%
      sf::st_intersection(., parks)
    # save it:
    saveRDS(catchments, paste0("data/mid/nhdhr_parks/nhdhr_park_",
                               "NHDPlusCatchment",
                               "_",
                               str_sub(files[i], 33, 36),
                               ".RDS"))
    
    # filter out and clip the flowline features within the park boundaries:
    flowlines <- sf::st_read(dsn = files[i], layer = "NHDFlowline") %>%
      sf::st_zm() %>%
      # All flowlines have catchments, so this speeds it up:
      dplyr::filter(NHDPlusID %in% catchments$NHDPlusID) %>%
      sf::st_intersection(., parks)
    saveRDS(flowlines, paste0("data/mid/nhdhr_parks/nhdhr_park_",
                              "NHDFlowline",
                              "_",
                              str_sub(files[i], 33, 36),
                              ".RDS"))
    
    # filter out and clip the waterbody features within the park boundaries:
    waterbodies <- sf::st_read(dsn = files[i], layer = "NHDWaterbody") %>%
      #st_cast("MULTIPOLYGON") %>%
      sf::st_zm() %>%
      sf::st_intersection(., parks)
    saveRDS(waterbodies, paste0("data/mid/nhdhr_parks/nhdhr_park_",
                                "NHDWaterbody",
                                "_",
                                str_sub(files[i], 33, 36),
                                ".RDS"))
    
    # filter out and clip the area features within the park boundaries:
    area <- sf::st_read(dsn = files[i], layer = "NHDArea") %>%
      #st_cast("MULTIPOLYGON") %>%
      sf::st_zm() %>%
      sf::st_intersection(., parks)
    saveRDS(area, paste0("data/mid/nhdhr_parks/nhdhr_park_",
                         "NHDArea",
                         "_",
                         str_sub(files[i], 33, 36),
                         ".RDS"))
  }
  
  print(paste0("HUC-", hucs, " done!"))
  
}

walk(hucs, figure_it_out)

# Did any not work?

no_dl <- list.files('data/mid/nhdhr_parks/') %>%
  as_tibble() %>%
  mutate(where=str_sub(value, -8, -5)) %>%
  group_by(where) %>%
  summarize(count = n()) %>%
  filter(count<4)
```

```{r}
projector <- function(nhdhr){
  
  feature <- readRDS(nhdhr) 
  if(sf::st_crs(feature) != 3857) {feature <- feature %>% sf::st_transform(3857)}
  return(feature)
  
} 

# BIND TOGETHER

# Catchments
nhdhr_park_catch <- list.files("data/mid/nhdhr_parks/", 
                               recursive = TRUE,
                               pattern = "NHDPlusCatchment",
                               full.names = TRUE) %>%
  
  map(~projector(.)) %>%
  bind_rows() %>%
  dplyr::select(UNIT_CODE,
                nhdplusid = NHDPlusID) %>%
  mutate(CATCH_TYPE = "NHDPlusHR")
saveRDS(nhdhr_park_catch, 'data/mid/nhdhr_park_catch.RDS')

# Flowlines
nhdhr_park_flows <- list.files("data/mid/nhdhr_parks/", 
                               pattern = "_NHDFlowline", 
                               recursive = TRUE,
                               full.names = TRUE) %>%
  map(~projector(.)) %>%
  bind_rows() %>%
  # add feature meta data (includes waterbody intermittency)
  left_join(., sf::st_read(dsn = "data/in/nhdplushr/01//NHDPLUS_H_0101_HU4_GDB.gdb",
                           layer = "NHDFCode"), by = "FCode")
saveRDS(nhdhr_park_flows, 'data/mid/nhdhr_park_flow.RDS')

# Waterbodies
nhdhr_park_waterbody <- list.files("data/mid/nhdhr_parks/", 
                                   pattern = "NHDWaterbody", 
                                   recursive = TRUE,
                                   full.names = TRUE) %>%
  map(~projector(.)) %>%
  bind_rows() %>%
  left_join(., sf::st_read(dsn = "data/in/nhdplushr/01//NHDPLUS_H_0101_HU4_GDB.gdb", 
                           layer = "NHDFCode"), by = "FCode")
saveRDS(nhdhr_park_waterbody, 'data/mid/nhdhr_park_waterbody.RDS')

# Areas
nhdhr_park_area <- list.files("data/mid/nhdhr_parks/", 
                              pattern = "NHDArea", 
                              recursive = TRUE,
                              full.names = TRUE) %>%
  map(~projector(.)) %>%
  bind_rows() %>%
  left_join(., sf::st_read(dsn = "data/in/nhdplushr/01//NHDPLUS_H_0101_HU4_GDB.gdb", layer = "NHDFCode"), 
            by = "FCode")
saveRDS(nhdhr_park_area, 'data/mid/nhdhr_park_area.RDS')
```

Sanity Check: did the upstream workflow work?
```{r}
test_join <- anti_join(parks, sf::st_drop_geometry(nhdhr_park_catch), by="UNIT_CODE")
rm(test_join)
# All in AK and VI, which checks out. Though, PEVI (Ohio) is in a weird NHD dead zone in Lake Erie...
```

There are some coastal/estuary/lake regions in parks that don't have catchments, similar to the problem identified at PEVI. So here I am just creating spatial features to represent these NHD catchment "dead zones" so we don't lose ATTAINS data that exists there:
```{r}
# make all the lil catchments into one big blob...
nhdhr_park_catch_dissolve <- nhdhr_park_catch %>%
  summarize()

# ... to use as an "eraser" for creating polygons where catchments don't
# exist in parks:
empty_park_space <- parks %>%
  sf::st_transform(3857) %>%
  sf::st_difference(., nhdhr_park_catch_dissolve) %>%
  select(UNIT_CODE) %>%
  mutate(CATCH_TYPE = "COASTAL",
         nhdplusid = NA)
 
park_catch <- empty_park_space %>%
  bind_rows(nhdhr_park_catch)
saveRDS(park_catch, 'data/mid/final_raw_catch_.RDS')
```

Subset and clip the ATTAINS geospatial data to only include assessment units within NPS park boundaries.
```{r}
park_catch <- readRDS('data/mid/final_raw_catch_.RDS') %>%
  sf::st_make_valid(.) %>% st_transform(3857)

npca_regions <- sf::st_read("data/in/npca_regions.shp") 

parks <- sf::st_read("data/in/nps_boundary.shp")

# Load in all raw geospatial ATTAINS data:
attains_areas <- readRDS('data/mid/attains_au_areas_.RDS') 

attains_lines <- readRDS('data/mid/attains_au_lines_.RDS')

attains_points <- readRDS('data/mid/attains_au_points_.RDS')

# Load in ATTAINS water quality standard parameter data:
attains_assmnt_parms <- readRDS("data/mid/attains_au_assmnt_parms.RDS")

# Load in CIP-like list of appropriately attributed ATTAINS/catchment combos:
right_dims_areas <- readRDS('data/mid/right_dims_areas_old.RDS')

right_dims_lines <- readRDS('data/mid/right_dims_lines_old.RDS')

coastal_waters <- st_read('data/bad/erase_temp.shp') %>% select(UNIT_CODE) %>% mutate(CATCH_TYPE = "COASTAL", nhdplusid = NA, SHAPE = geometry) %>% sf::st_transform(3857) 

# subset area features
nps_attains_areas_raw <- attains_areas %>% 
  subsetATTAINS(layer = ., sub_by = park_catch, type = "area") %>%
  mutate(assessment_type = "AREA") %>%
  # Link up info for catchments with the right catchment attribution
  left_join(., right_dims_areas, by = c("nhdplusid","assessmentunitidentifier")) %>%
  # keep only catchment-AU combos that made the cut ^^ OR are coastal:
  filter(!is.na(catchment_area)|CATCH_TYPE == "COASTAL") %>%
  mutate(combo = paste0(nhdplusid, "-", assessmentunitidentifier))

nps_attains_areas_near_wb <- nps_attains_areas_raw %>%
  # I have found that "area" ATTAINS features are the most coarse resolution
  # of all ATTAINS features. Therefore, this step is to verify that ATTAINS
  # areas within catchments are actually linked to an existing water feature
  # in the park. This layer I am joining by is the clipped NHD-HR features within park units.
  # Meaning, only keep ATTAINS area features that directly contain
  # an NHD HR water feature:
  st_join(., readRDS('data/mid/nhdhr_park_waterbody.RDS'), left = FALSE) %>% 
  select(combo)

nps_attains_areas_near_flowlines <- nps_attains_areas_raw %>%
  # Only select area features within 10 meters of a water feature
  st_join(., readRDS('data/mid/nhdhr_park_flow.RDS'), left = FALSE) %>%
  select(combo)

nps_attains_areas_near_areas <- nps_attains_areas_raw %>%
  # Only select area features within 10 meters of a water feature
  st_join(., readRDS('data/mid/nhdhr_park_area.RDS'), left = FALSE) %>%
  select(combo)

nps_attains_areas_near_coasts <- nps_attains_areas_raw %>%
  # Only select area features within 10 meters of a water feature
  st_join(., select(coastal_waters, CATCH_TYPE), left = FALSE) %>%
  select(combo)

nps_attains_areas <- nps_attains_areas_raw %>%
  dplyr::filter(combo %in% c(nps_attains_areas_near_wb$combo, nps_attains_areas_near_flowlines$combo,                       nps_attains_areas_near_areas$combo, nps_attains_areas_near_coasts$combo)) %>%#|
           # Cannot do this exercise in states without NHD:
           #STATE %in% c("AK","HI","PR","VI","AS","GU","MP")) %>%
  select(-combo)

# subset line features
nps_attains_lines <- attains_lines %>%
  subsetATTAINS(layer = ., sub_by = park_catch, type = "line") %>%
  data.table() %>%
  mutate(assessment_type = "LINE") %>%
  # Link up info for catchments with the right catchment attribution
  left_join(., right_dims_lines, by = c("nhdplusid","assessmentunitidentifier")) %>%
  # keep only catchment-AU combos that made the cut ^^ OR are coastal:
  filter(!is.na(catchment_length)|CATCH_TYPE == "COASTAL")

# subset point features (simple, no thresholds/clipping needed)
nps_attains_points <- attains_points %>%
  subsetATTAINS(layer = ., sub_by = park_catch, type = "point") %>%
  mutate(assessment_type = "POINT")

# this represents all assessment units (areal, point, linear) that are physically within the park boundaries
# split by catchment, as a data frame
nps_all_attains <- bind_rows(data.table(nps_attains_areas), data.table(nps_attains_lines), data.table(nps_attains_points)) %>%
    data.table(.) %>%
    dplyr::left_join(.,
                     # remove duplicate/unnecessary columns:
                     dplyr::select(attains_assmnt_parms, -c(assmnt_joinkey, organizationid, submissionid, orgtype, tas303d, reportingcycle, waterbodyreportlink, GLOBALID)),
                     by = "assessmentunitidentifier", multiple = "all")
saveRDS(nps_all_attains, 'data/mid/nps_attains_catchment_table_.RDS')

# Next link all of this information to our park catchment layer so it can be geospatially represented:
nps_attains_to_catchment <- park_catch %>%
  data.table::data.table(.) %>%
  dplyr::left_join(nps_all_attains,
                   by = c("nhdplusid", "UNIT_CODE"), multiple = "all") %>%
  dplyr::mutate(attains = ifelse(is.na(assessmentunitidentifier), "NO ATTAINS DATA", "ATTAINS DATA")) %>%
  sf::st_as_sf(.)

nps_attains_to_catchment$catchment_area_fin <- sf::st_area(nps_attains_to_catchment, by_element = TRUE)

saveRDS(nps_attains_to_catchment, 'data/mid/nps_attains_catchment_geospatial_.RDS')
```