---
title: "Untitled"
author: "Katie Willi"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Identifying appropriate catchment-assessment unit combinations
```{r}
# Load in park boundaries (from NPS IRMA)
parks <- sf::st_read("data/in/nps_boundary/nps_boundary.shp") %>%
  sf::st_transform(3857)

# List of HUC-2s to map over:
hucs <- (c("01","02","03","04","05","06","07","08","09","10",
           "11","12","13","14","15","16","17","18","19","20",
           "21","22"))

park_areas <- readRDS('data/mid/attains_au_areas.RDS') %>%
  .[parks,] %>%
  st_transform(4269) 

park_lines <- readRDS('data/mid/attains_au_lines.RDS') %>%
  .[parks,] %>%
  st_transform(4269)

## Total length and areas:
park_areas$total_area <- sf::st_area(park_areas, by_element = TRUE)
park_lines$total_length <- sf::st_length(park_lines, by_element = TRUE)

figure_it_out <- function(hucs){
  
  # Where to find our HUC-4 datasets:
  nhdhr <- paste0('data/in/nhdplushr/', hucs, "/")
  
  files <- list.files(nhdhr, pattern = "GDB.gdb", full.names=TRUE)
  
  # Clip NHD-HR features within park units across individual HUC-4 files:
  for(i in 1:length(files)){
    
    # filter out and clip the flowline features within the park boundaries:
    catchments <- sf::st_read(dsn = files[i], layer = "NHDPlusCatchment")
    catchments$square_meters <- sf::st_area(catchments, by_element = TRUE)
    
    try(areas <- park_areas %>%
          st_intersection(., catchments) %>%
          select(nhdplusid = NHDPlusID, total_area, assessmentunitidentifier, square_meters))
    try(areas$catchment_area <- sf::st_area(areas, by_element = TRUE))
    
    
    try(lines <- park_lines %>%
          st_intersection(.,catchments) %>%
          select(nhdplusid = NHDPlusID, total_length, assessmentunitidentifier, square_meters))
    try(lines$catchment_length <- sf::st_length(lines, by_element = TRUE))
    
    
    # save it:
    try(saveRDS(st_drop_geometry(lines), paste0("data/mid/catchment_au_test/lines_",
                                                str_sub(files[i], 33, 36), 
                                                ".RDS")))
    
    try(saveRDS(st_drop_geometry(areas), paste0("data/mid/catchment_au_test/areas_",
                                                str_sub(files[i], 33, 36), 
                                                ".RDS")))
  }
  
  print(paste0("HUC-", hucs, " done!"))
  
}

walk(hucs, figure_it_out)

right_dims_lines <- list.files('data/mid/catchment_au_test/', pattern = "lines", full.names = TRUE) %>%
  map(~readRDS(.)) %>%
  bind_rows() %>%
  # remove line features from catchments that have less than 30 meters within:
  filter(as.numeric(catchment_length) >= 30) 
saveRDS(right_dims_lines, 'data/mid/right_dims_lines.RDS')



right_dims_areas <- list.files('data/mid/catchment_au_test/', pattern = "areas", full.names = TRUE) %>%
  map(~readRDS(.)) %>%
  bind_rows() %>%
  filter(((as.numeric(catchment_area)/as.numeric(total_area)) >= 0.01) | 
           as.numeric(catchment_area) >= (as.numeric(square_meters)*.5))
saveRDS(right_dims_areas, 'data/mid/right_dims_areas.RDS')
